--- 
title: "Introduction to Data Science"
author: "DS-SL"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: ds-sl/ds_book
description: Book on an introducion to data-science
---

This is a test version of Introduction using bookdown-demo template from remote

* With an error: erased the bs4_book from output.yml # bookdown::bs4_book: default
* On Terminal
```
(base) hsuzuki-imacpro-3132:ds_book hsuzuki$ cd ../
(base) hsuzuki-imacpro-3132:bookdown hsuzuki$ git init ds_book
Reinitialized existing Git repository in /Users/hsuzuki/Documents/computer/r/bookdown/ds_book/.git/
(base) hsuzuki-imacpro-3132:ds_book hsuzuki$ git remote add origin git@github-sub:ds-sl/ds_book.git
(base) hsuzuki-imacpro-3132:ds_book hsuzuki$ git push origin main
Counting objects: 12, done.
Delta compression using up to 16 threads.
Compressing objects: 100% (12/12), done.
Writing objects: 100% (12/12), 2.04 KiB | 2.04 MiB/s, done.
Total 12 (delta 8), reused 0 (delta 0)
remote: Resolving deltas: 100% (8/8), completed with 4 local objects.
To github-sub:ds-sl/ds_book.git
   a3a0557..d977b47  main -> main
```

I don't know why it does not work
Restarted!

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
